---
title: "Vehicle MPG Prediction"
author: "Max Gribov"
date: "June 24, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Predicting Miles per Gallon for a Vehicle

This application attempts to estimate the MPG value for a given vehicle, based on a linear model trained on *mtcars* dataset.

In testing, a linear model using vehicle's weight, transmission type, and 1/4 mile time was found to be the most accurate.

The application also plots the values of the user's vehicle against the data used to train the model.


## Training the Model

- First, we build a model with all the variables

```{r train1, echo = TRUE}
lm_full <- lm(mpg ~ ., data=mtcars)
```

- Next, we use step() function to find most optimal model

```{r train2, echo = TRUE}
lm_step <- step(lm_full, trace=0)
```

- The final model uses *wt*, *qsec*, and *am* variables.

```{r details1, echo = TRUE}
summary(lm_step)$coeff
```


## Model Details

This final model has high R-Squared value and low residual standard error

```{r details2, echo = TRUE}
summary(lm_step)$r.squared
summary(lm_step)$sigma
```


## Sample MPG Prediction

Example of using the model to predict MPG for a vehicle with weight of 3000 lbs, manual transmission, and 17 second 1/4 mile time

```{r pred, echo = TRUE}
my <- data.frame(wt=3, am=1, qsec=17)
predict(lm_step, my)
```

